---
title: "Examples"
author: "David Cooley"
date: "`r Sys.Date()`"
output: 
    html_document:
        toc: true
        toc_float: true
        number_sections: false
        theme: flatly
header-includes: 
    - \usepackage{tikz}
    - \usetikzlibrary{arrows}
vignette: >
  %\VignetteIndexEntry{Rcpp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "# ",
  echo = TRUE, 
  eval = TRUE
  )
```

```{r, eval = T, warning=FALSE, message = FALSE}
library(sfheaders)
library(sf) ## for nice printing
```


### R

The hierarchy of `sf` objects goes

1. sfg - simple feature geometry
2. sfc - simple feature collection (a collection of sfg)
3. sf - simple feature object (sfc with data attributes)

#### sfg

The `sfg_` group of functions assume the input is a single geometry.

```{r}

sfg_point( 1:2 )
sfg_point( 1:3 )
sfg_point( 1:4 )

sfg_linestring( 1:4 )

df <- data.frame(
  x = c(1,1,4,4,1)
  , y = c(1,4,4,1,1)
)
sfg_linestring(df)

sfg_polygon(df)

```

#### sfc

The `sfc_` group of functions let you specify an 'id' value to identify individual geometries. (Except for `sfc_point()`, in this case every row is an individual geometry).

```{r}

df <- data.frame(
  id = c(1,1,2,2,3)
  , x = c(1,1,4,4,1)
  , y = c(1,4,4,1,1)
)

sfc_point( df )

sfc_multipoint( df, multipoint_id = "id" )

sfc_linestring( df, linestring_id = "id" )

## leaving the 'id' field blank
sfc_polygon( df )

```


#### sf

The `sf_` functions also let you specify an 'id' value, but in this case the id is retained and kept on the object


```{r}

df <- data.frame(
  id = c(1,1,2,2,3)
  , x = c(1,1,4,4,1)
  , y = c(1,4,4,1,1)
)

sf_point( df )

sf_multipoint( df, multipoint_id = "id" )

sf_linestring( df, linestring_id = "id" )

## leaving the 'id' field blank
sf_polygon( df )

```


```r
n <- 1e5
df <- data.frame(
  id = rep(1:(n/5), each = 5)
  , x = rnorm(n)
  , y = rnorm(n)
)

library(data.table)
library(microbenchmark)

dt <- as.data.table( df )
microbenchmark(

  dt = {
    sf <- dt[
      , {
        geometry <- sf::st_linestring( x = matrix( c( x, y ), ncol = 2, byrow = T ))
        geometry <- sf::st_sf( geometry = sf::st_sfc( geometry ) )
      }
      , by = id
    ]
    sf <- sf::st_as_sf( sf )
  },
  
  sfheaders = {
    sfh <- sfheaders::sf_linestring(
      obj = df
      , linestring_id = "id"
    )
  },
  times = 5
)

# Unit: milliseconds
#      expr        min         lq       mean     median         uq        max neval
#        dt 6599.67479 6654.12357 6779.23543 6750.19807 6833.46262 7058.71809     5
# sfheaders   21.07775   21.30438   23.20592   23.21665   25.06429   25.36654     5

```
